Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-07-05 manuscript/response_to_reviews.Rmd

- Line 275-280: those profiles were assumed a priori in the introduction and are common to any forest. They are indeed interesting to characterise the forest, but they do not add to individual tree variability. You could think to send Figure 2 to an appendix, in consequence, and use figures to show more specific results related to your individual tree analyses.

[*issue #71*](https://github.com/SCBI-ForestGEO/McGregor_climate-sensitivity-variation/issues/71)

- Line 330-331: any evidence to support this? It looks rather speculative. As suggested above, does any species particularly show positive Rt or positive Rt are randomly distributed in your trees?

**IM I have done this for Rt, see below. I notice we don't have negative at all, just above or below 0. I'm assuming this is what the reviewer is referring to? Assuming this should be SI plot? Please let me know if you think this figure should be altered at all. **
![Rt across species](tables_figures/rt_across_species.png)

### 2020-07-05 manuscript/climate_sensitivity_draft.Rmd
Update climate_sensitivity_draft.Rmd

Many studies have shown that within species, large trees tend to be more affected by drought. Greater growth reductions for larger trees was first shown on a global scale by @bennett_larger_2015, and subsequent studies have reinforced this finding (*e.g.*, @stovall_tree_2019; @hacket-pain_consistent_2016). It has yet to be resolved which of several potential underlying mechanisms most strongly shape size trends in drought response. First, tree height may be a primary driver. Taller trees face the biophysical challenge of lifting water greater distances against the effects of gravity and friction [@mcdowell_relationships_2011; @mcdowell_darcys_2015; @ryan_hydraulic_2006; @couvreur_water_2018]. Vertical gradients in stem and leaf traits--including smaller and thicker leaves (higher leaf mass per area, LMA), greater resistance to hydraulic dysfunction (*i.e.*, more negative water potential at 50% loss of hydraulic conductivity,more negative P50), and lower hydraulic conductivity at greater heights [@couvreur_water_2018; @koike_leaf_2001; @mcdowell_relationships_2011]--enable trees to become tall [@couvreur_water_2018]. Indeed, tall trees require xylem of greater hydraulic efficiency in their basal portions, such that xylem conduit diameters are wider in taller trees within and across species [@olson_plant_2018; @liu_hydraulic_2019]. Wider xylem conduits make large trees more vulnerable to embolism during drought [@olson_plant_2018], and traits conducive to efficient water transport may also lead to poor ability to recover from or re-route water around embolisms [@roskilly_conflicting_2019]. Second, larger trees may have lower drought resistance because they tend to occupy more exposed canopy positions, where they are exposed to higher solar radiation, greater wind speeds, and lower relative humidity (e.g., @koike_leaf_2001; @kunert_revised_2017). Subcanopy trees tend to fare better specifically due to the benefits of a buffered environment [@pretzsch_drought_2018]. Third, large trees tend to have larger root systems, which potentially counteracts some of the biophysical challenges they face by allowing greater access to water; however, it appears that this effect is usually insufficient to offset the costs of height and/or crown exposure. Finally, tree size-related responses to drought can be modified by species' traits and their distribution across size classes [@meakem_role_2018; @liu_hydraulic_2019]. Understanding the mechanisms driving the greater relative growth reductions of larger trees during drought will require sorting out the interactive effects of height, canopy position, root water access, and species' traits.

>>>>

Many studies have shown that within species, large trees tend to be more affected by drought. Greater growth reductions for larger trees was first shown on a global scale by @bennett_larger_2015, and subsequent studies have reinforced this finding (*e.g.*, @stovall_tree_2019; @hacket-pain_consistent_2016). It has yet to be resolved which of several potential underlying mechanisms most strongly shape size trends in drought response. First, tree height may be a primary driver. Taller trees face the biophysical challenge of lifting water greater distances against the effects of gravity and friction [@mcdowell_relationships_2011; @mcdowell_darcys_2015; @ryan_hydraulic_2006; @couvreur_water_2018]. Vertical gradients in stem and leaf traits--including smaller and thicker leaves (higher leaf mass per area, LMA), greater resistance to hydraulic dysfunction (*i.e.*, more negative water potential at 50% loss of hydraulic conductivity,more negative P50), and lower hydraulic conductivity at greater heights [@couvreur_water_2018; @koike_leaf_2001; @mcdowell_relationships_2011]--enable trees to become tall [@couvreur_water_2018]. Indeed, tall trees require xylem of greater hydraulic efficiency in their basal portions, such that xylem conduit diameters are wider in taller trees within and across species [@olson_plant_2018; @liu_hydraulic_2019]. Wider xylem conduits make large trees more vulnerable to embolism during drought [@olson_plant_2018], and traits conducive to efficient water transport may also lead to poor ability to recover from or re-route water around embolisms [@roskilly_conflicting_2019]. Second, larger trees may have lower drought resistance because they tend to occupy more exposed canopy positions, where they experience higher solar radiation, greater wind speeds, and lower relative humidity (**REFS--KAT**). Subcanopy trees tend to fare better specifically due to the benefits of a buffered environment [@pretzsch_drought_2018]. Third, large trees tend to have larger root systems, which potentially counteracts some of the biophysical challenges they face by allowing greater access to water; however, it appears that this effect is usually insufficient to offset the costs of height and/or crown exposure. Finally, tree size-related responses to drought can be modified by species' traits and their distribution across size classes [@meakem_role_2018; @liu_hydraulic_2019]. Understanding the mechanisms driving the greater relative growth reductions of larger trees during drought will require sorting out the interactive effects of height, canopy position, root water access, and species' traits.
